\cvsection{Peer-Reviewed Publications}

\begin{rSection}{}

  \textbf{† indicates equal contribution}

  % \underline{\textbf{Occhialini, G.}}; Wendlandt, A. E. Kinetics, thermodynamics, and emergence in stereoediting reactions, \textit{Invited review, In preparation.}

  % \underline{\textbf{Occhialini, G.†}}; Moulton. K.†; Wendlandt, A. β-glucosylation to access β-mannosides, \textit{In preparation.}

  % Zhang, R.†; \underline{\textbf{Occhialini, G.†}}; Zhang, J.; Barbour, J.; Scola, P.; Ramirez, A.; Wendlandt, A. E. Heterocycle-specific C-H alkylation of pyridazine, \textit{In preparation.}

  % Gorelik, D.†; Gong, G.†; \underline{\textbf{Occhialini, G.}}; Barbour, J.; Gu, X.; Wendlandt, A. E. Acceptorless dehydrogenation for the expedient synthesis of highly functionalized phenols and arenes. \textit{In preparation.}

  Zhang, S.; \underline{\textbf{Occhialini, G.}}; Carder, H. M.; de Kleijne, F. F. J.; Wendlandt, A. E. Steady state tuning under kinetic network control: selective epimerization of GlcNAc to GalNAc. \textit{Under Evaluation\textemdash{}Nature Chem.}

  Carder, H. M.†; \underline{\textbf{Occhialini, G.†}}; Bistoni, G.; Riplinger, C.; Kwan, E. E.; Wendlandt, A. E. The sugar cube: Network control and emergence in stereoediting reactions. \textit{Science} \textbf{2024}, \textit{385}, 456\textemdash{}463.
  
  Gu, X.†; Zhang, Y.-A.†; Wang, L.; Ye, X.; \underline{\textbf{Occhialini, G.}}; Barbour, J.; Pentelute, B. L.; Wendlandt, A. E. Synthesis of Non-Canonical Amino Acids through Dehydrogenative Tailoring. \textit{Nature} \textbf{2024}, \textit{634}, 456\textemdash{}463.
  
  \underline{\textbf{Occhialini, G.}}; Palani, V.; Wendlandt, A. E. Catalytic, contra-thermodynamic positional alkene isomerization. \textit{J. Am. Chem. Soc.} \textbf{2022}, 144, 145\textemdash{}152.
  
  Thompson, C. M. †; \underline{\textbf{Occhialini, G.†}}; McCandless, G. T.; Alahakoon, S. B.; Cameron, V.; Nielsen, S. O.; Smaldone, R. A. Computational and Experimental Studies on the Effects of Monomer Planarity on Covalent Organic Framework Formation. \textit{J. Am. Chem. Soc.} \textbf{2017}, 139, 10506\textemdash{}10513.
  
  Alahakoon, S. B.†; \underline{\textbf{Occhialini, G.†}}; McCandless, G. T.; Karunathilake, A. A. K.; Nielsen, S. O.; Smaldone, R. A. Experimental and theoretical insight into the effect of fluorine substituents on the properties of azine linked covalent organic frameworks. \textit{CrystEngComm} \textbf{2017}, 19, 4882\textemdash{}4885.
  
  Xiong, H.; Zuo, H.; Yan, Y.; \underline{\textbf{Occhialini, G.}}; Zhou, K.; Wan, Y.; Siegwart, D. J. High-contrast fluorescence detection of metastatic breast cancer including bone and liver micrometastases via size-controlled pH-activatable water-soluble probes. \textit{Adv. Mat.} \textbf{2017}, 29, 1700131.
  
  Alahakoon, S. B.; Thompson, C. M.; \underline{\textbf{Occhialini, G.}}; Smaldone, R. A. Design principles for covalent organic frameworks in energy storage applications. \textit{ChemSusChem} \textbf{2017}, 10, 2116\textemdash{}2129

  Alahakoon, S. B.; Thompson, C. M.; Nguyen, A. X.; \underline{\textbf{Occhialini, G.}}; McCandless, G. T.; Smaldone, R. A. An azine-linked hexaphenylbenzene based covalent organic framework. \textit{Chem. Comm.} \textbf{2016}, \textit{52}, 2843\textemdash{}2845

\end{rSection}